Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars

### 2020-05-22 manuscript/manuscript.tex
Pass ball to TT

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{2}$
Adriano Agnello,$^{3}$\newauthor
Dominique Sluse,$^{4}$
Chris Fassnacht,$^{5}$
Matthew W. Auger,$^{6}$
Kenneth C. Wong,$^{7}$ \newauthor
Sherry H. Suyu,$^{8,9,10}$
Takahiro Morishita,$^{11}$
\pink{
Cristian E. Rusu,$^{12,13,14}$
Aymeric Galan,$^{15}$}\newauthor
and et al.
\\
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan\\
$^{13}$Subaru Telescope, National Astronomical Observatory of Japan, 650 N Aohoku Pl, Hilo, HI 96720\\
$^{14}$Department of Physics, University of California, Davis, 1 Shields Avenue, Davis, CA 95616, USA\\
$^{15}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland\\
$^{13}$TBC
}

@@

\subsection{Data Preparation and Modelling Setup}

@@

We also compare our measurement to the previous reconstructions by \citet{Ding2017b}. Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$. The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}. However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}. This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein). \pink{Despite that \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, their inferred host surface brightness is computed by collecting the \sersic\ light within a aperture where host was reconstructed; the aperture size is decided by the mask region in the image plane.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies. While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.

@@

@@

In addition, we adopt simple stellar populations to derive the stellar mass. For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift. The lack of color information by necessity increases the error budget in the inferred \mstar. \pink{Once again, the same approach is adopted in D20, and thus our stellar masses are consistent with the D20's 32 high redshift AGN regarding this point.}
\pink{We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies. As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104. For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data. We interpret this as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}

@@

\pink{The strong lensing can help to extend the measurements of the AGN host to even higher redshift. It is worth noting that the lensed AGN adopted by this study are adopted from the H0LiCOW project which only focuses on the moment of the peak of the AGN luminosity function. In fact, the observation of \hst\ could even unveil the lensed AGN host of  BRI0952$-$0115 at $z=4.5$.}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{2}$
Adriano Agnello,$^{3}$\newauthor
Dominique Sluse,$^{4}$
Chris Fassnacht,$^{5}$
Matthew W. Auger,$^{6}$
Kenneth C. Wong,$^{7}$ \newauthor
Sherry H. Suyu,$^{8,9,10}$
Takahiro Morishita,$^{11}$
\pink{
Cristian E. Rusu,$^{12,13,14}$
Aymeric Galan,$^{15}$}
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan\\
$^{13}$Subaru Telescope, National Astronomical Observatory of Japan, 650 N Aohoku Pl, Hilo, HI 96720\\
$^{14}$Department of Physics, University of California, Davis, 1 Shields Avenue, Davis, CA 95616, USA\\
$^{15}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland
}

@@

\subsection{Data Preparation and Modelling Setup}\label{sec:Modelling}

@@

We also compare our measurement to the previous reconstructions by \citet{Ding2017b}. Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$. The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}. However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}. This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein). \pink{Note that \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, and then the inferred host surface brightness is computed by collecting the \sersic\ light within the aperture where host was reconstructed. This aperture in the source plane is decided by the mask region in the image plane, thus a smaller mask region could lead the inference of the host brightness fainter. For a consistency check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (here) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies. While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.

@@

\pink{In this work, we used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling. Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth. We apply this method to the entire systems to allow the self-consistency within our sample, despite that four systems (HE0435, RXJ1131, WFI2033, and SDSS1206) have been analyzed by H0LiCOW collaboration with slope value provided. For a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW's inference. The results are the following (here {\it V.S.} H0LiCOW): HE0435~($2.032\pm 0.07$ {\it V.S.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it V.S.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it V.S.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it V.S.} $\sim1.95$). These consistent results demonstrate the efficiency of the systematic uncertainty estimates in this work.}

@@

In addition, we adopt simple stellar populations to derive the stellar mass. For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift. The lack of color information by necessity increases the error budget in the inferred \mstar. \pink{Once again, the same approach is adopted in D20, and thus our stellar masses are consistent with the D20's 32 high redshift AGN regarding this point.}

\pink{We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies. As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104 through filter F160W. For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data.
If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our point.
We interpret this as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}

@@

\pink{The strong lensing can even help to extend the measurements of the AGN host to higher redshift. It is worth noting that the lensed AGN adopted by this study are adopted from the H0LiCOW project which only focuses on the moment of the peak of the AGN luminosity function. In fact, the observation of \hst\ could even unveil the lensed AGN host of  BRI0952$-$0115 at $z=4.5$.}
